Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-11 outputs/paper/paper.qmd
Update some codes

```
Figure 2 A, abortion law applicable age ~,

Technology enhancement in medical field allows the abortion to be held more easily compared to 1980, 1990s. This change allow the young women who can afford the abortion or vice versa who can't afford giving birth to get the abortion. In the meantime, due to the advancement of technology, women at relatively old age can give the birth in their late 30s or even 40s. As well as change in child birth policy and health maintenance was eased compared to the old days in 1980s, 1990s, that promotes women at age older than 30 who are relatively financially stable have high willingness to give births, showing ascending pattern in birth rates over the 40 years.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-trendssub-table
#| tbl-cap: "Trends in Birth Rates by Population Race and Ethnicity"

# Load necessary libraries
library(dplyr)
library(knitr)
library(kableExtra)

# Filter the data to include years starting from 1990
filtered_data <- data %>%
  filter(year >= 1990)

# Select the required columns and rename them
selected_data <- filtered_data %>%
  select(Year = year, White = brate_whitenh, Black = brate_blacknh, Hispanic = brate_hisp)

# Print the table using additional styling
kable(selected_data, caption = "Trends in Birth Rates by Population Race and Ethnicity (ages 15-44)", format = "html") %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c("","Births per 1,000 women" = 3))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-trendssub-graph
#| fig-cap: "Trends in Birth Rates by Population Race and Ethnicity"

# Load required libraries
library(dplyr)
library(ggplot2)

# Refer to the table a
# Assume selected_data contains the relevant data

# Create bar graphs for each racial/ethnic group
bar_plot <- ggplot(selected_data, aes(x = Year)) +
  geom_bar(aes(y = Hispanic, fill = "Hispanic"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Black, fill = "Black"), stat = "identity", position = "stack") +
  geom_bar(aes(y = White, fill = "White"), stat = "identity", position = "stack") +
  labs(x = "Year",
       y = "Births per 1,000 women relevant population subgroup") +
  scale_fill_manual(values = c(Hispanic = "grey", Black = "orange", White = "blue"),
                    name = "Race and ethnicity") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(1990, 2020, by = 5), minor_breaks = seq(1990, 2020, by = 1)) +
  ylim(0, 120)

# Print the bar plot
print(bar_plot)
```
Figure 3 B, major religion of Hispanic, Black, White  religious reason of each race and ethnicity.

@@

Might include Map or not depending on the sources and references I find, see how long it'll gonna be.

Figure 1 Trend in US Birth Rates, not just the Great Recession was there another events? 
abortion law, law enforcement dates, economic crisis other than great recession

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

>>>>

@@

In panel A of @fig-bratepop-graph can be interpreted as the proportion of US women using a contraceptive method rose from 56% in 1982 to 60% in 1988 and 64% in 1995. This trends in contraceptive use have implications for downward shifts in preganancy rates which ultimately affects birth rates (Piccinino and Mosher 1998). 
Moreover, states began to pass parental involvement laws to limit minors' confidential access to abortion (Myers 2022). Meaning that although by 1980 judicial precedent established that minors can consent to abortion services absent a valid restriction, as of 1980, minors had a limitation on abortion which possibly draw correlation between the more usage in contraceptive measurements to prevent the pregnancy.

As a result, legal access to abortion and contraceptive in the 1960s and

In panel B of @fig-bratepop-graph, major religion of Hispanic, Black, White  religious reason of each race and ethnicity.

@@
